\bf A Principal Manifold-based Framework for Comparisons of Group-Level Manifold Estimates

### 2025-04-09 paper/main.tex
Updates from Overleaf

%\documentclass[12pt]{amsart}
\documentclass[11pt,reqno]{article}
%\usepackage{cases}

%\RequirePackage[numbers]{natbib}
%\RequirePackage[authoryear]{natbib}%% uncomment this for author-year citations
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}%% uncomment this for coloring bibliography citations and linked URLs
\RequirePackage{graphicx}%% uncomment this for including figures

\usepackage[
  backend=biber,
  style=authoryear
]{biblatex}

\addbibresource{references.bib}

\usepackage{setspace}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage[perpage,symbol*]{footmisc}
\usepackage{float}
\usepackage{hyperref}
\usepackage{color}  
\usepackage{tikz}
\usepackage{caption}
\usepackage{subcaption}

\usepackage{algorithm2e}

%\usepackage{natbib}
%\bibliographystyle{abbrvnat}
%\setcitestyle{authoryear,open={(},close={)}}
\usepackage{authblk}

\usepackage{csquotes}
\usepackage[english]{babel}

\renewcommand{\baselinestretch}{1.0}
\setlength{\oddsidemargin}{-0.5cm}
\setlength{\evensidemargin}{-0.5cm}
\renewcommand{\topmargin}{-2cm}
\renewcommand{\oddsidemargin}{0mm}
\renewcommand{\evensidemargin}{0mm}
\renewcommand{\textwidth}{180mm}
\renewcommand{\textheight}{240mm}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\T}{\intercal}
\newcommand{\commentout}[1]{}

\newcommand{\kmedit}[1]{{\color{purple}  #1}}
\newcommand{\meng}[1]{{\color{purple} \sf $\clubsuit\clubsuit\clubsuit$ Kun Meng: [#1]}}
\newcommand{\Meng}[1]{\margMa{(Kun Meng) #1}}

\newcommand{\zielinski}[1]{{\color{blue} \sf $\spadesuit\spadesuit\spadesuit$ Rob Zielinski: [#1]}}

@@

@@

\title{Hierarchical Principal Manifold Estimation}
\author[1]{Robert Zielinski}
\author[2]{Kun Meng}
\author[1]{Ani Eloyan}
\affil[1]{Department of Biostatistics, Brown University}
\affil[2]{Division of Applied Mathematics, Brown University}

\maketitle

\doublespacing

\section*{Abstract} \label{s:abstract}

\section{Introduction} \label{s:hpme_intro}

@@

The embedding function which maps from the $d$-dimensional manifold to $D$-dimensional ambient space is represented as $\psi(\mathbf{y}_{jq})$, which can be modeled as 
\begin{equation}
  \mathbf{x}_{jq} = \psi(\mathbf{y}_{jq}, t_j) = f_p(\mathbf{y}_{jq}, t_{j}) + f_{g(j)}(\mathbf{y}_{jq}, t_{j}) + f_{i(j)}(\mathbf{y}_{jq}, t_{j}) + f_j(\mathbf{y}_{jq}) + \epsilon_{jq}. \label{eq:2}
\end{equation}
The embedding map $\psi(\mathbf{y})$ is associated with a projection index $\kappa_{\psi}(\mathbf{x}): \mathbb{R}^{D} \to \mathbb{R}^{d}$, which, informally, outputs the $d$-dimensional parameterization $\mathbf{y}$ that minimizes $\|\mathbf{x} - \psi(\mathbf{y})\|_{\mathbb{R}^{D}}$ and follows the generalized definition of projection indices given in \cite{mengPrincipalManifoldEstimation2021}.

@@

\nocite{*}
%\bibliographystyle{plain}
%\bibliography{references}
\printbibliography

>>>>

\documentclass[12pt]{article}
\usepackage{algorithm2e}
\usepackage{amscd}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{authblk}
\usepackage[english]{babel}
\usepackage{bm}
\usepackage{caption}
\usepackage{color}
\usepackage{float}
\usepackage[perpage, symbol*]{footmisc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{url}

\newcommand{\blind}{1}
\graphicspath{{figures/}}

\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-1in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.7in}%
\addtolength{\topmargin}{-1in}%

\pdfminorversion=4

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\T}{\intercal}

@@

\setcitestyle{aysep={}}

@@

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if1\blind
{
  \title{\bf A Principal Manifold-based Framework for Comparisons of Group-Level Manifold Estimates}
  \author{
    Robert Zielinski\hspace{.2cm}\\
    Department of Biostatistics, Brown University\\
    Kun Meng \\
    Division of Applied Mathematics, Brown University\\
    and \\
    Ani Eloyan \\
    Department of Biostatistics, Brown University\\
    for the Alzheimer's Disease Neuroimaging Initiative\thanks{Data used in preparation of this article were obtained from the Alzheimer's Disease Neuroimaging Initiative (ADNI) database (adni.loni.usc.edu). As such, the investigators within the ADNI contributed to the design and implementation of ADNI and/or provided data but did not participate in analysis or writing of this report. A complete listing of ADNI investigators can be found at \href{http://adni.loni.usc.edu/wp-content/uploads/how_to_apply/ADNI_Acknowledgement_List.pdf}{\texttt{http://adni.loni.usc.edu/wp-content/uploads/how\_to\_apply/ADNI\_Acknowledgement\_List.pdf}}}}
  \maketitle
} \fi

\if0\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf A Principal Manifold-based Framework for Comparisons of Group-Level Manifold Estimates}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
Structural magnetic resonance imaging (MRI) data is frequently used to detect and monitor the progression of neurodegenerative conditions, such as Alzheimer's disease (AD). While 
\end{abstract}

\noindent%
{\it Keywords:}  Alzheimer's disease, smoothing spline, magnetic resonance imaging
\vfill

\newpage
\spacingset{1.9}
\section{Introduction} \label{s:hpme_intro}

@@

The embedding function which maps from the $d$-dimensional manifold to $D$-dimensional ambient space is represented as $\psi(\mathbf{y}_{jq})$, which can be modeled as 
\begin{equation}
  \mathbf{x}_{jq} = \psi(\mathbf{y}_{jq}, t_j) = f_p(\mathbf{y}_{jq}, t_{j}) + f_{g(j)}(\mathbf{y}_{jq}, t_{j}) + f_{i(j)}(\mathbf{y}_{jq}, t_{j}) + f_j(\mathbf{y}_{jq}) + \epsilon_{jq}j. \label{eq:2}
\end{equation}
The embedding map $\psi(\mathbf{y})$ is associated with a projection index $\kappa_{\psi}(\mathbf{x}): \mathbb{R}^{D} \to \mathbb{R}^{d}$, which, informally, outputs the $d$-dimensional parameterization $\mathbf{y}$ that minimizes $\|\mathbf{x} - \psi(\mathbf{y})\|_{\mathbb{R}^{D}}$ and follows the generalized definition of projection indices given in \cite{mengPrincipalManifoldEstimation2021}.

@@

\bibliographystyle{jasa}
\bibliography{references}
